Presolving for\\ Mixed-Integer Semidefinite Optimization

### 2020-12-14 tex/MISDP-Presolving/MISDPpresolving.tex
add remark about RIP in dimension two

\begin{question}
  One idea is to perform spatial branching on the diagonal entries
  $X_ii$. Does this help to solve the problem?
\end{question}

>>>>

\begin{question}
  One idea is to perform spatial branching on the diagonal entries
  $X_{ii}$. Does this help to solve the problem?
\end{question}

\begin{remark}
  For the case of~$k=2$, an optimal solution~$X$ consists of a single 2 by
  2 nonzero submatrix, and all other entries are 0. Let
  \begin{align*}
    \tilde{X} =  \begin{pmatrix}
      X_{11} & X_{21} \\
      X_{21} & X_{22}
    \end{pmatrix}
  \end{align*}
  be a 2 by 2 submatrix of~$X$. The trace constraint then
  reads~$X_{11} + X_{22} = 1$, and the psd constraint~$X \succeq 0$
  simplifies to~$X_{11},\, X_{22} \geq 0$, and $X_{11}X_{22}\geq
  X_{21}^2$. If~$X_{21} = 0$, then either~$X_{11} = 1$ or~$X_{22} = 1$,
  depending on their coefficients in the objective function.
  If~$X_{21} \neq 0$, aggregate~$X_{22} = 1 - X_{11}$. In this case, the
  solution set is given by a disc centered at $(1/2,\,0)$ with
  radius~$1/2$, where~$X_{11}$ is the first coordinate and~$X_{21}$ the
  second. Optimizing in direction of the objective function yields an
  optimal solution.
\end{remark}
